On verifying AhirV2 generated VHDL using software testbenches

### 2011-08-25 v2/CtestBench/docs/CtestBench.tex
Release area updated.

Look at the subdirectory ``example'' which contains the files ``prog.c'' and
``testbench.c''.  A Makefile and README are also present.  Its all quite
self-explanatory.

\end{document}

>>>>

The following Makefile builds a software-only testbench
executable, and also converts the system described in prog.c
to VHDL.  The same testbench can be used to test the VHDL
also.
\begin{verbatim}
# build software version of testbench 
# (to check the "desired behaviour")
IOLIB_INCLUDE=../../iolib/include
IOLIB_LIB=../../iolib/lib
SOCKETLIB_INCLUDE=../../CtestBench/include
SOCKETLIB_LIB=../../CtestBench/lib
VHDL_LIB=../../vhdl
VHDL_VHPI_LIB=../../CtestBench/vhdl
all: SW HW

# compile with SW defined.
# note the use of IOLIB in building the testbench.
SW: prog.c prog.h testbench.c 
        gcc -c -DSW -I$(IOLIB_INCLUDE) prog.c
        gcc -c -DSW -I$(IOLIB_INCLUDE) testbench.c
        gcc -o testbench_sw prog.o testbench.o -L$(IOLIB_LIB) -lio -lpthread

# five steps from C to vhdl simulator.
HW: c2llvmbc llvmbc2aa aa2vc vc2vhdl vhdlsim

# C to llvm byte-code.. use clang.
c2llvmbc: prog.c prog.h testbench.c
        clang -std=gnu89 -I$(IOLIB_INCLUDE) -emit-llvm -c prog.c
        #llvm-dis prog.o
        opt -O3	 prog.o > prog.opt.o
        llvm-dis prog.opt.o

# llvm byte-code to Aa..
llvmbc2aa:  prog.opt.o
        llvm2aa prog.opt.o | vcFormat >  prog.opt.o.aa

# Aa to vC
aa2vc: prog.opt.o.aa
        Aa2VC -O -C prog.opt.o.aa | vcFormat > prog.opt.o.aa.vc

# vC to VHDL
vc2vhdl: prog.opt.o.aa.vc
        vc2vhdl -C -e ahir_system -w -s ghdl\
                -T accumulate -t set_sum -t get_sum\
                -f prog.opt.o.aa.vc 
        vhdlFormat < ahir_system.unformatted_vhdl > ahir_system.vhdl
        vhdlFormat < ahir_system_test_bench.unformatted_vhdl\
                    > ahir_system_test_bench.vhdl

# build testbench and ghdl executable
# note the use of SOCKETLIB in building the testbench.
vhdlsim: ahir_system.vhdl ahir_system_test_bench.vhdl\
           testbench.c vhdlCStubs.h vhdlCStubs.c
        gcc -c vhdlCStubs.c -I./ -I$(SOCKETLIB_INCLUDE)
        gcc -c testbench.c -I./ -I$(SOCKETLIB_INCLUDE)
        gcc -o testbench_hw testbench.o vhdlCStubs.o\
               -L$(SOCKETLIB_LIB) -lSocketLib -lpthread
        ghdl --clean
        ghdl --remove
        ghdl -i --work=ahir  $(VHDL_LIB)/ahir.vhdl
        ghdl -i --work=ieee_proposed  $(VHDL_LIB)/ieee_proposed.vhdl
        ghdl -i --work=work $(VHDL_VHPI_LIB)/Utility_Package.vhdl
        ghdl -i --work=work $(VHDL_VHPI_LIB)/Vhpi_Package.vhdl
        ghdl -i --work=work ahir_system.vhdl
        ghdl -i --work=work ahir_system_test_bench.vhdl
        ghdl -m --work=work -Wc,-g -Wl,-L$(SOCKETLIB_LIB)\
                 -Wl,-lVhpi ahir_system_test_bench

clean:
        rm -f *.o* *.cf *.*vhdl vhdlCStubs.*\
             *.vcd in_data* out_data* testbench_sw\
              testbench_hw ahir_system_test_bench\
              vhpi.log

PHONY: all clean	
\end{verbatim}
To test the software, run testbench\_sw.  To verify the hardware (using
the VHDL simulator GHDL), start testbench\_sw in one shell, and then start ahir\_system\_test\_bench
in a different shell.
\end{document}
